The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2021-12-17 src/ms.tex
proposed section authors

@@

@@

\begin{itemize}
    \item Support for representing and transforming velocity data in coordinates, epoch propagation (v3.0)
    \item Improved support for astronomical time series: TimeSeries object (v3.2), Box Least Squares periodogram (v3.1)
    \item Overall improved support of Quantity throughout numpy (v4.0) and scipy
    \item Native support for Time, Quantity, and SkyCoord objects in Astropy tables
    \item TODO: something about WCS, SpectralCoord?
\end{itemize}

@@

New CoCo and election overview.

@@

Overview and statistics of contributors. Changes since v2.0.

@@

@@

New funding sources.
% Funding received:
% - Moore
% - NASA

@@

@@

New packages and major updates!

\subsection{Connections with observatories}

JWST (motivated by excitement around the launch?)

Gemini

@@

@@

Current status and scope

Vision for the future (review what we said in v2.0 paper)

User forums and engagement with user base

\subsection{Challenges}

Attracting new contributors when the code has become quite complex,
Contributor to maintainer mentoring,
Long-term / sustained funding for maintaining infrastructure,
...

>>>>

\newcommand{\secauthor}[1]{{\color{blue}Author:~\textit{#1}}}
\newcommand{\secunfilled}{{\color{red}Author:~\textit{Looking for volunteers!}}}

@@

\secauthor{Tom Robitaille}

Summarize a few notable things in v5.0 as compared to the last LTS release.

@@

\secauthor{Nathaniel Starkman, Marten van Kerkwijk}

Summarize major pieces of development since the last paper (since v2.0). A few
ideas (taken from What's New pages) below, but feel free to expand on or remove
from this list:
\begin{itemize}
    \item Support for representing and transforming velocity data in coordinates, epoch propagation (v3.0)
    \item Improved support for astronomical time series: TimeSeries object (v3.2), Box Least Squares periodogram (v3.1)
    \item Overall improved support of Quantity throughout numpy (v4.0) and scipy
    \item Native support for Time, Quantity, and SkyCoord objects in Astropy tables
    \item TODO: something about WCS, SpectralCoord?
\end{itemize}

@@

\secauthor{Erik Tollerud}

Briefly summarize new procedures and governance structure, new CoCo, election
process overview, etc.

@@

\secunfilled

Overview and statistics of contributors. Highlight changes since v2.0.

@@

\subsection{Inclusion, Diversity, and Equity Programs} \label{sec:project-ide}

\secauthor{Lía Corrales}

@@

\secauthor{Aarya Patil}

Summarize funding sources (Moore, NASA) and amounts and what this has been used
for.

@@

\secunfilled

@@

\secauthor{Matt Craig, Brett Morris}

Highlight a few new affiliated packages and major updates to existing ones.
Include a big table of all affiliated packages and references (as in v2.0
paper).

\subsection{Connections with data archives}

\secauthor{Adam Ginsburg}

Summary of Astroquery and engagement with archives. Cite astroquery paper.

\subsection{Connections with Observatories and Missions}

Brief summary of efforts in observatory- or mission-driven development that have
contributed to Astropy, and vice versa.

JWST
\secunfilled

Gemini
\secunfilled

Cherenkov Telescope Array
\secauthor{Axel Donath, Max Noethe}

Rubin Observatory
\secunfilled

@@

\secauthor{Clara Brasseur}

Overview of roadmap and some highlights.

@@

\secauthor{Lía Corrales, David Shupe + Learn team}

\begin{itemize}
\item Current status and scope
\item Vision for the future (review what we said in v2.0 paper)
\item User forums and engagement with user base
\item Workshops
\end{itemize}

\subsection{Current and Future Challenges}

\secunfilled

\begin{itemize}
\item Attracting new contributors when the code has become quite complex,
\item Contributor to maintainer mentoring,
\item Long-term / sustained funding for maintaining infrastructure,
\item ...
\end{itemize}
